Machine Learning Approaches for Accurate Diamond Price Prediction\\ \thanks{Final Project Report ECS-171: \textbf{Group 21}}

### 2024-06-08 paper/main.tex
added

\author{
\IEEEauthorblockN{Aditya Mittal}
\IEEEauthorblockA{\textit{Department of Statistics} \\
\textit{University of California, Davis}\\
Davis, United States \\
adimittal@ucdavis.edu}
\and
\IEEEauthorblockN{Andrew Yeow}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{University of California, Davis}\\
Davis, United States \\
XXX}
\and
\IEEEauthorblockN{Yifan Cui}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{University of California, Davis}\\
Davis, United States \\
harcui@ucdavis.edu}
\and
\IEEEauthorblockN{Nandini Koladi}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{University of California, Davis}\\
Davis, United States \\
XXX}
\and
\IEEEauthorblockN{Eshan Toshniwal}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{University of California, Davis}\\
Davis, United States \\
XXX}
}

>>>>

\author{
\IEEEauthorblockN{Aditya Mittal}
\IEEEauthorblockA{\textit{Department of Statistics} \\
\textit{University of California, Davis}\\
Davis, United States \\
adimittal@ucdavis.edu}
\and
\IEEEauthorblockN{Andrew Yeow}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{University of California, Davis}\\
Davis, United States \\
acyeow@ucdavis.edu}
\and
\IEEEauthorblockN{Yifan Cui}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{University of California, Davis}\\
Davis, United States \\
harcui@ucdavis.edu}
\and
\IEEEauthorblockN{Nandini Koladi}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{University of California, Davis}\\
Davis, United States \\
skodali@ucdavis.edu}
\and
\IEEEauthorblockN{Eshan Toshniwal}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{University of California, Davis}\\
Davis, United States \\
etoshniwal@ucdavis.edu}
}
